---
title: "Milestone one"
author: "ChufanZhou;JiachengYu;XinyuLi;XuZou;YuqianChen."
date: "2022-11-18"
output:
  prettydoc::html_pretty:
    theme: cyman
    highlight: github
  html_document: default
  rticles::ctex:
    latex_engine: xelatex
    keep_tex: true
    fig_caption: yes
    number_sections: yes
    toc: yes
    includes:
      in_header: setup/ctex_header.tex
      before_body: setup/ctex_format.tex
classoption: [a4paper, oneside, zihao=-4, UTF8]
fontsize: 12pt
header-includes:
- \addbibresource{./reference/refs.bib} 
- \renewcommand*{\bibfont}{\zihao{5}}
- \usepackage{indentfirst}
- \setlength{\parindent}{2em}

---

```{r message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dataset Introduction

>- NYC Real-Time Traffic Speed Data
>- 24GB dataset on Kaggle https://www.kaggle.com/datasets/aadimator/nyc-realtime-traffic-speed-data
>- Contains ‘real-time’ traffic information, including average speed, travel time and location of speed detectors

## Question: 
**Which streets in New York have a higher rate of vehicles over speed**

## Data Description

>- 64 million samples and 13 variables in this dataset 
>- Care about *“id” “speed” “link_id” “borough” “link_name”* variables
>- *"borough" *represents the name of the New York district, including Brooklyn, Bronx, Manhattan, Queens and Staten Island
>- *"link_name"* represents the names of the streets

## Data Split: Divide dataset by “LINK_ID” into 160 small dataset
*mydata = read.csv("DOT_Traffic_Speeds_NBE.csv", header = TRUE)*<br />
*linkid = unique(mydata$LINK_ID)* <br />
*for(i in linkid){* <br />
  *newdata = mydata[mydata$LINK_ID==i, ]* <br />
  *write.csv(newdata, paste("linkid_", as.character(i), ".csv", sep=""),* <br /> *row.names=FALSE)* <br />
*}* <br />

```{r message=FALSE, warning=FALSE, include=FALSE,echo=FALSE}
library(ggplot2)
library(tidyverse)
library(dplyr)
library(knitr)
library(gcookbook)
```

## Read Data
```{r uspop,echo=TRUE}
#Select one of the split csv to display the data set.
mydata = read.csv("/Users/yujiacheng/Desktop/605\ final/linkid_4329472.csv", header = TRUE)
mydata_head=mydata[1:5,c(1,2,6,12,13)]
knitr::kable(head(mydata_head))
```
## Statistical methods

```{r}
mydata_new <- mydata[which(mydata$SPEED !=0),]
mydata_new <- mydata_new[which(mydata_new$SPEED <120),]
sum(mydata_new["SPEED"]>60)/nrow(mydata_new)
```


>- The rate of vehicles'exceeding speed passing on this streets is 0.024%.

## Github Link: https://github.com/XXinyu-0907/STAT605_final_project_nyc_traffic
